QRF Covariate Selection

### 2020-02-05 analysis/R_scripts/fit_qrf_model.Rmd
added metadata for GAAs. Read in from QRFcapacity repo

@@

write_rds(gaa_covars,
          "../data/derived_data/gaa_covars.rds")
write_rds(mod_data_weights,
          "../data/derived_data/mod_data_weights.rds")
write_rds(model_svy_df,
          "../data/derived_data/model_svy_df.rds")
write_rds(all_preds,
          "../data/derived_data/all_preds.rds")

>>>>

# get some meta data for GAAs
gaa_meta = readxl::read_excel('../../../QRFcapacity/data/raw/master_sample_pts/GAA_Metadata_20150506.xlsx') %>%
              mutate(FieldName = recode(FieldName,
                                        'ChanlType' = 'Channel_Type')) %>%
              bind_rows(tibble(Covariate = "S2_02_11",
                               Name = "NorWeST Avg. Aug. Temp",
                               Units = "C",
                               SpatialScale = "Site-300m"))

@@

write_rds(gaa_covars,
          "../data/derived_data/gaa_covars.rds")
write_rds(gaa_meta,
          "../data/derived_data/gaa_metadata.rds")
write_rds(mod_data_weights,
          "../data/derived_data/mod_data_weights.rds")
write_rds(model_svy_df,
          "../data/derived_data/model_svy_df.rds")
write_rds(all_preds,
          "../data/derived_data/all_preds.rds")
